---
title: "parallel analysis"
output: html_document
date: "8088-08-88"
---

```{r setup, include=FALSE}
library(dplyr)
library(foreach)
 library(doParallel)
 library(parallel)
library(tidyverse)
library(kableExtra)
library(multcomp)

library(tidybayes)
library(MuMIn)

library(rstan)
library(brms)
library(lme4)
```

Setup cluster

```{r setup, include=FALSE}
 n.cores <- parallel::detectCores() - 4
my.cluster <- parallel::makeCluster(
  n.cores,
  type = "FORK"
  )

#register it to be used by %dopar%
doParallel::registerDoParallel(cl = my.cluster)

#stopCluster(my.cluster)
```

```{r}
course_enroll <- 50
seed=12345
set.seed (seed)
```

Simulation function

```{r}
sim_data <- function(n){
    Sim<-data.frame(Race = sample(c(0,1,2,3, 4,5,6, 7,8, 9),n-40, replace = TRUE, prob=c(7380,22,156,320, 3100,224,138, 2048,3816, 28710)),
                      women = sample(c(0,1),n-40, replace = TRUE, prob=c(.64,.36)),
                      FG = sample(c(0,1),n-40, replace = TRUE, prob=c(.64,.36)))
minimums <- data.frame(Race = rep(0:9, 4),
                      women = rep(c(rep(0,10),rep(1,10)), 2),
                      FG = rep(c(rep(0,20), rep(1,20)),1))
    
    Sim <- rbind(Sim,minimums)
    
Sim <- Sim  %>%
  mutate(Asian = ifelse(Race==0 | Race ==1 | Race ==2| Race==3,1,0),
         Asian_Black = ifelse(Race==1,1,0),
         Asian_Hispanic = ifelse(Race==2,1,0),
         Asian_White = ifelse(Race==3,1,0),
         
         Black = ifelse(Race==4 | Race==5 |Race==6 |Race==1,1,0),
         Black_Hispanic = ifelse(Race==5,1,0),
         Black_White = ifelse(Race==6,1,0),
         
         Hispanic = ifelse(Race==7 | Race==8 | Race==2| Race==5,1,0),
         Hispanic_White = ifelse(Race==8,1,0),
         
         White = ifelse(Race==9 |Race ==3| Race==6| Race==8,1,0))
         
Sim <- Sim  %>%
  mutate(cluster = (1000000 + 100000*(Asian) +10000*(Black) +1000*(Hispanic) +100*(White) + 10*(women) + 1*(FG)),
 score = 47 - 3*FG -10*women -6*Black -10*Hispanic +2*White +3*FG*women +1*White*Hispanic -1*FG*Black +2*FG*Hispanic +2*FG*White -2*women*Black + 1*women*Hispanic -4*women*White - 1*FG*White*Hispanic + 5*women*White*Hispanic + 4*FG*women*Black + 1*FG*women*White - 1* FG*women*White*Hispanic + rnorm(n, sd = 20))
    Sim$course = rep(1:(n/course_enroll))
    
course_dif <- rnorm(n/course_enroll, sd = 10)
course_dif <- rep(course_dif, course_enroll)
Sim <- Sim %>%
  mutate(course_diff = course_dif,
         score = score + course_diff)


return(Sim)}
```

Function for running Bayesian HLM models

```{r}

HLM_bay_fun <- function(sim_data){
temp <- brm(formula= score ~ women*(Asian*(Black + Hispanic + White) + Black*(Hispanic + White) + Hispanic*White)*FG + (1|course), data=sim_data)

return(temp)}
```

Function for running MAIHDA models

```{r}
MAIHDA_fun <- function(sim_data){
temp <- brm(formula= score ~ 1 + women + Black + Hispanic + White + FG + (1|course) + (1|cluster), data=sim_data)

return(temp)}
```

Get priors
```{r}
example <- sim_data(1000)

get_prior(formula= score ~ women*(Asian*(Black + Hispanic + White) + Black*(Hispanic + White) + Hispanic*White)*FG + (1|course), data=example)
```

Function for calculating outcomes in HLM_bay models pt 1

```{r}
pred_scores_HLM_bay <- function(posterior) {
  
posterior <- posterior %>%
  rename_with(~gsub(":", "_",.x, fixed = TRUE)) %>%
  rename_with(~gsub("b_", "",.x, fixed = TRUE))

#pretest
Estimates <- posterior %>% 
  mutate(#Asian 1, 3, 3, 7
    "CG Asian men" = Asian, 
         "CG Asian women" = Asian + 
          women + women_Asian,
          "FG Asian men" = Asian + 
            FG + Asian_FG,
          "FG Asian women" = Asian +
           women + women_Asian +
           FG + women_FG + women_Asian_FG + Asian_FG ,
    #Asian Black 3, 7, 7, 15
    "CG Asian Black men" = Asian + Black + Asian_Black, 
         "CG Asian Black women" = Asian + Black + Asian_Black + 
          women + women_Asian + women_Black + women_Asian_Black,
          "FG Asian Black men" = Asian + Asian_Black +
            FG + Black + Black_FG + Asian_FG + Asian_Black_FG,
          "FG Asian Black women" = Asian + Black + Asian_Black + 
      women + women_Black + women_Asian + women_Asian_Black +
           FG + Asian_FG + Black_FG + women_FG + women_Black_FG + Asian_Black_FG + women_Asian_FG + women_Asian_Black_FG,
    #Asian Hispanic 3, 7, 7, 15
    "CG Asian Hispanic men" = Asian + Hispanic + Asian_Hispanic, 
         "CG Asian Hispanic women" = Asian + Hispanic + Asian_Hispanic + 
          women + women_Asian + women_Hispanic + women_Asian_Hispanic,
          "FG Asian Hispanic men" = Asian + Asian_Hispanic +
            FG + Hispanic + Hispanic_FG + Asian_FG + Asian_Hispanic_FG,
          "FG Asian Hispanic women" = Asian + Hispanic + Asian_Hispanic + 
      women + women_Hispanic + women_Asian + women_Asian_Hispanic +
           FG + Asian_FG + Hispanic_FG + women_FG + women_Hispanic_FG + Asian_Hispanic_FG + women_Asian_FG + women_Asian_Hispanic_FG,
        #Asian White 3, 7, 7, 15
    "CG Asian White men" = Asian + White + Asian_White, 
         "CG Asian White women" = Asian + White + Asian_White + 
          women + women_Asian + women_White + women_Asian_White,
          "FG Asian White men" = Asian + Asian_White +
            FG + White + White_FG + Asian_FG + Asian_White_FG,
          "FG Asian White women" = Asian + White + Asian_White + 
      women + women_White + women_Asian + women_Asian_White +
           FG + Asian_FG + White_FG + women_FG + women_White_FG + Asian_White_FG + women_Asian_FG + women_Asian_White_FG,
    #Black 1, 3, 3, 7
    "CG Black men" = Black, 
         "CG Black women" = Black + 
          women + women_Black,
          "FG Black men" = Black + 
            FG + Black_FG,
          "FG Black women" = Black +
           women + women_Black +
           FG + women_FG + women_Black_FG + Black_FG ,
       #Black Hispanic 3, 7, 7, 15
    "CG Black Hispanic men" = Black + Hispanic + Black_Hispanic, 
         "CG Black Hispanic women" = Black + Hispanic + Black_Hispanic + 
          women + women_Black + women_Hispanic + women_Black_Hispanic,
          "FG Black Hispanic men" = Black + Black_Hispanic +
            FG + Hispanic + Hispanic_FG + Black_FG + Black_Hispanic_FG,
          "FG Black Hispanic women" = Black + Hispanic + Black_Hispanic + 
      women + women_Hispanic + women_Black + women_Black_Hispanic +
           FG + Black_FG + Hispanic_FG + women_FG + women_Hispanic_FG + Black_Hispanic_FG + women_Black_FG + women_Black_Hispanic_FG,
      #Black White 3, 7, 7, 15
    "CG Black White men" = Black + White + Black_White, 
         "CG Black White women" = Black + White + Black_White + 
          women + women_Black + women_White + women_Black_White,
          "FG Black White men" = Black + Black_White +
            FG + White + White_FG + Black_FG + Black_White_FG,
          "FG Black White women" = Black + White + Black_White + 
      women + women_White + women_Black + women_Black_White +
           FG + Black_FG + White_FG + women_FG + women_White_FG + Black_White_FG + women_Black_FG + women_Black_White_FG,
    # #Hispanic 1, 3, 3, 7
    "CG Hispanic men" = Hispanic, 
         "CG Hispanic women" = Hispanic + 
          women + women_Hispanic,
          "FG Hispanic men" = Hispanic + 
            FG + Hispanic_FG,
          "FG Hispanic women" = Hispanic +
           women + women_Hispanic +
           FG + women_FG + women_Hispanic_FG + Hispanic_FG ,
    #     #White 1, 3, 3, 7
    "CG White men" = White, 
         "CG White women" = White + 
          women + women_White,
          "FG White men" = White + 
            FG + White_FG,
          "FG White women" = White +
           women + women_White +
           FG + women_FG + women_White_FG + White_FG ,
    #      White Hispanic 3, 7, 7, 15
    "CG White Hispanic men" = White + Hispanic + Hispanic_White, 
         "CG White Hispanic women" = White + Hispanic + Hispanic_White + 
          women + women_White + women_Hispanic + women_Hispanic_White,
          "FG White Hispanic men" = White + Hispanic_White +
            FG + Hispanic + Hispanic_FG + White_FG + Hispanic_White_FG,
          "FG White Hispanic women" = White + Hispanic + Hispanic_White + 
      women + women_Hispanic + women_White + women_Hispanic_White +
           FG + White_FG + Hispanic_FG + women_FG + women_Hispanic_FG + Hispanic_White_FG + women_White_FG + women_Hispanic_White_FG,
         ) %>% 
  pivot_longer("CG Asian men":"FG White Hispanic women",
               names_to = "soc_id") %>%
  group_by(soc_id) %>%
  mean_qi(value) %>% 
  mutate_if(is.double, round, digits = 3)%>%
  rename(Score = value,
         group = soc_id) %>%
  mutate(SE = (.upper-.lower)/4,
         model = "HLM_bay",
         CG = word(group, 1), #This makes a new variable called "Race" and it uses the first word in the "group" variable for its values. You'll need to make sure this makes sense for your data.
         Race = word(group, 2), #This makes a new variable called "Gender" and it uses the second word in the "group" variable for its values. You'll need to make sure this makes sense for your data.
         Gender = word(group, 3))

return(Estimates)
}
```

Function for calculating outcomes in HLM_bay models pt 2

```{r}
est_HLM_bay_fun <- function(scores) {
temp <- posterior_samples(scores, c("b_", "bsp_","r_cluster"))
pred_scores_HLM_bay_out <- pred_scores_HLM_bay(temp)

return(pred_scores_HLM_bay_out) }
```

Function for calculating outcomes in MAIHDA models pt 1

```{r}
pred_scores_MAIHDA <- function(posterior) {

posterior <- posterior %>%
  rename_with(~gsub(":", "_",.x, fixed = TRUE)) %>%
  rename_with(~gsub("b_", "",.x, fixed = TRUE)) %>%
  rename_with(~gsub("r_cluster[1", "c",.x, fixed = TRUE)) %>%
  rename_with(~gsub(",Intercept]", "",.x, fixed = TRUE))

#pretest
Estimates <- posterior %>% 
  mutate(#Asian
    "CG Asian men" = Intercept + c100000, 
         "CG Asian women" = Intercept + women + c100010,
          "FG Asian men" = Intercept + FG + c100001,
          "FG Asian women" = Intercept + women + FG + c100011,
    #Asian Black
    "CG Asian Black men" = Intercept + Black + c110000, 
         "CG Asian Black women" = Intercept + Black + women + c110010,
          "FG Asian Black men" = Intercept + Black + FG + c110001,
          "FG Asian Black women" = Intercept + Black + women + FG + c110011,
        #Asian Hispanic
    "CG Asian Hispanic men" = Intercept + Hispanic + c101000, 
         "CG Asian Hispanic women" = Intercept + Hispanic + women + c101010,
          "FG Asian Hispanic men" = Intercept + Hispanic + FG + c101001,
          "FG Asian Hispanic women" = Intercept + Hispanic + women + FG + c101011,
            #Asian White
    "CG Asian White men" = Intercept + White + c100100, 
         "CG Asian White women" = Intercept + White + women + c100110,
          "FG Asian White men" = Intercept + White + FG + c100101,
          "FG Asian White women" = Intercept + White + women + FG + c100111,

    #Black
    "CG Black men" = Intercept + Black + c010000,
         "CG Black women" = Intercept + Black + women + c010010,
         "FG Black men" = Intercept + Black + FG + c010001,
         "FG Black women" = Intercept + Black + women + FG + c010011,
        #Black Hispanic
    "CG Black Hispanic men" = Intercept + Black + Hispanic + c011000,
         "CG Black Hispanic women" = Intercept + Black + women + Hispanic + c011010,
         "FG Black Hispanic men" = Intercept + Black + FG + Hispanic + c011001,
         "FG Black Hispanic women" = Intercept + Black + women + FG + Hispanic + c011011,
        #Black White
    "CG Black White men" = Intercept + Black + White + c010100,
         "CG Black White women" = Intercept + Black + women + White + c010110,
         "FG Black White men" = Intercept + Black + FG + White + c010101,
         "FG Black White women" = Intercept + Black + women + FG + White + c010111,
    #Hispanic
    "CG Hispanic men" = Intercept + Hispanic + c001000,
         "CG Hispanic women" = Intercept + Hispanic + women + c001010,
         "FG Hispanic men" = Intercept + Hispanic + FG + c001001,
         "FG Hispanic women" = Intercept + Hispanic + women + FG + c001011,
    #White
    "CG White men" = Intercept + White + c000100,
         "CG White women" = Intercept + White + women + c000110,
         "FG White men" = Intercept + White + FG + c000101,
         "FG White women" = Intercept + White + women + FG + c000111,
        #White Hispanic
             "CG White Hispanic men" = Intercept + White + Hispanic + c001100,
         "CG White Hispanic women" = Intercept + White + Hispanic + women + c001110,
         "FG White Hispanic men" = Intercept + White + Hispanic + FG + c001101,
         "FG White Hispanic women" = Intercept + White + Hispanic + women + FG + c001111) %>% 
  
  pivot_longer("CG Asian men":"FG White Hispanic women",
               names_to = "soc_id") %>%
  group_by(soc_id) %>%
  mean_qi(value) %>% 
  mutate_if(is.double, round, digits = 3) %>%
  rename(Score = value,
         group = soc_id) %>%
  mutate(SE = (.upper-.lower)/4,
         model = "MAIHDA",
         CG = word(group, 1), #This makes a new variable called "Race" and it uses the first word in the "group" variable for its values. You'll need to make sure this makes sense for your data.
         Race = word(group, 2), #This makes a new variable called "Gender" and it uses the second word in the "group" variable for its values. You'll need to make sure this makes sense for your data.
         Gender = word(group, 3))

return(Estimates)
}
```

Function for calculating outcomes in MAIHDA models pt 2

```{r}
est_MAIHDA_fun <- function(scores) {
temp <- posterior_samples(scores, c("b_", "bsp_","r_cluster"))
pred_score_MAIHDA_out <- pred_scores_MAIHDA(temp)

return(pred_score_MAIHDA_out) }
```

Function to string them together

```{r}
sim_HLM_fun <- function(n, set_seed) {
#sim the data
   set.seed (set_seed)
  data.sim <- sim_data(n)
#Run the models
HLM_bay_mod <- HLM_bay_fun(data.sim)
MAIHDA_mod <- MAIHDA_fun(data.sim)

#get the estimates
HLM_bay_est <- est_HLM_bay_fun(HLM_bay_mod)
MAIHDA_est <- est_MAIHDA_fun(MAIHDA_mod)

#Filter for the categories we want and rename them
HLM_bay_est <- HLM_bay_est  %>%
  dplyr::select(group, Score, SE, CG, Race, Gender, model)

MAIHDA_est <- MAIHDA_est  %>%
  dplyr::select(group, Score, SE, CG, Race, Gender, model)

final <- rbind(HLM_bay_est,MAIHDA_est)
final$N <- n
return(final)}
```

Forloop simulating data 500
Missing iterations failed to run do to some groups having n=0
```{r include=FALSE}
Sys.time()
out_500_1 <- foreach(i=1:50) %dopar% {sim_HLM_fun(500,i)}
save(out_500_1, file="out_500_1.rda")
Sys.time()

out_500_2 <- foreach(i=51:100) %dopar% {sim_HLM_fun(500,i)}
save(out_500_2, file="out_500_2.rda")

out_500_3 <- foreach(i=101:150) %dopar% {sim_HLM_fun(500,i)}
save(out_500_3, file="out_500_3.rda")

out_500_4 <- foreach(i=151:200) %dopar% {sim_HLM_fun(500,i)}
save(out_500_4, file="out_500_4.rda")

out_500_5 <- foreach(i=201:250) %dopar% {sim_HLM_fun(500,i)}
save(out_500_5, file="out_500_5.rda")

out_500_6 <- foreach(i=251:300) %dopar% {sim_HLM_fun(500,i)}
save(out_500_6, file="out_500_6.rda")

out_500_7 <- foreach(i=301:350) %dopar% {sim_HLM_fun(500,i)}
save(out_500_7, file="out_500_7.rda")

out_500_8 <- foreach(i=351:400) %dopar% {sim_HLM_fun(500,i)}
save(out_500_8, file="out_500_8.rda")

out_500_9 <- foreach(i=401:450) %dopar% {sim_HLM_fun(500,i)}
save(out_500_9, file="out_500_9.rda")

out_500_10 <- foreach(i=451:500) %dopar% {sim_HLM_fun(500,i)}
save(out_500_10, file="out_500_10.rda")

out_500_11 <- foreach(i=501:550) %dopar% {sim_HLM_fun(500,i)}
save(out_500_11, file="out_500_11.rda")

out_500_12 <- foreach(i=551:600) %dopar% {sim_HLM_fun(500,i)}
save(out_500_12, file="out_500_12.rda")

out_500_13 <- foreach(i=601:650) %dopar% {sim_HLM_fun(500,i)}
save(out_500_13, file="out_500_13.rda")

out_500_14 <- foreach(i=651:700) %dopar% {sim_HLM_fun(500,i)}
save(out_500_14, file="out_500_14.rda")

out_500_15 <- foreach(i=701:750) %dopar% {sim_HLM_fun(500,i)}
save(out_500_15, file="out_500_15.rda")

out_500_16 <- foreach(i=751:800) %dopar% {sim_HLM_fun(500,i)}
save(out_500_16, file="out_500_16.rda")

out_500_17 <- foreach(i=801:850) %dopar% {sim_HLM_fun(500,i)}
save(out_500_17, file="out_500_17.rda")

out_500_18 <- foreach(i=851:900) %dopar% {sim_HLM_fun(500,i)}
save(out_500_18, file="out_500_18.rda")

out_500_19 <- foreach(i=901:950) %dopar% {sim_HLM_fun(500,i)}
save(out_500_19, file="out_500_19.rda")

out_500_20 <- foreach(i=951:1000) %dopar% {sim_HLM_fun(500,i)}
save(out_500_20, file="out_500_20.rda")
```

Forloop simulating data 1000

```{r include=FALSE}
#1000 here
Sys.time()
out_1000_1 <- foreach(i=1:50) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_1, file="out_1000_1.rda")
Sys.time()

out_1000_2 <- foreach(i=51:100) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_2, file="out_1000_2.rda")

out_1000_3 <- foreach(i=101:150) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_3, file="out_1000_3.rda")

out_1000_4 <- foreach(i=151:200) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_4, file="out_1000_4.rda")

out_1000_5 <- foreach(i=201:250) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_5, file="out_1000_5.rda")

out_1000_6 <- foreach(i=251:300) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_6, file="out_1000_6.rda")

out_1000_7 <- foreach(i=301:350) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_7, file="out_1000_7.rda")

out_1000_8 <- foreach(i=351:400) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_8, file="out_1000_8.rda")

out_1000_9 <- foreach(i=401:450) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_9, file="out_1000_9.rda")

out_1000_10 <- foreach(i=451:500) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_10, file="out_1000_10.rda")

out_1000_11 <- foreach(i=501:550) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_11, file="out_1000_11.rda")

out_1000_12 <- foreach(i=551:600) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_12, file="out_1000_12.rda")

out_1000_13 <- foreach(i=601:650) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_13, file="out_1000_13.rda")

out_1000_14 <- foreach(i=651:700) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_14, file="out_1000_14.rda")

out_1000_15 <- foreach(i=701:750) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_15, file="out_1000_15.rda")

out_1000_16 <- foreach(i=751:800) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_16, file="out_1000_16.rda")

out_1000_17 <- foreach(i=801:850) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_17, file="out_1000_17.rda")

out_1000_18 <- foreach(i=851:900) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_18, file="out_1000_18.rda")

out_1000_19 <- foreach(i=901:950) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_19, file="out_1000_19.rda")

out_1000_20 <- foreach(i=951:1000) %dopar% {sim_HLM_fun(1000,i)}
save(out_1000_20, file="out_1000_20.rda")
```


```{r include=FALSE}
#5000 here
Sys.time()
out_5000_1 <- foreach(i=1:50) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_1, file="out_5000_1.rda")
Sys.time()

out_5000_2 <- foreach(i=51:100) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_2, file="out_5000_2.rda")

out_5000_3 <- foreach(i=101:150) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_3, file="out_5000_3.rda")

out_5000_4 <- foreach(i=151:200) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_4, file="out_5000_4.rda")

out_5000_5 <- foreach(i=201:250) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_5, file="out_5000_5.rda")

out_5000_6 <- foreach(i=251:300) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_6, file="out_5000_6.rda")

out_5000_7 <- foreach(i=301:350) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_7, file="out_5000_7.rda")

out_5000_8 <- foreach(i=351:400) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_8, file="out_5000_8.rda")

out_5000_9 <- foreach(i=401:450) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_9, file="out_5000_9.rda")

out_5000_10 <- foreach(i=451:500) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_10, file="out_5000_10.rda")

out_5000_11 <- foreach(i=501:550) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_11, file="out_5000_11.rda")

out_5000_12 <- foreach(i=551:600) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_12, file="out_5000_12.rda")

out_5000_13 <- foreach(i=601:650) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_13, file="out_5000_13.rda")

out_5000_14 <- foreach(i=651:700) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_14, file="out_5000_14.rda")

out_5000_15 <- foreach(i=701:750) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_15, file="out_5000_15.rda")

out_5000_16 <- foreach(i=751:800) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_16, file="out_5000_16.rda")

out_5000_17 <- foreach(i=801:850) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_17, file="out_5000_17.rda")

out_5000_18 <- foreach(i=851:900) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_18, file="out_5000_18.rda")

out_5000_19 <- foreach(i=901:950) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_19, file="out_5000_19.rda")

out_5000_20 <- foreach(i=951:1000) %dopar% {sim_HLM_fun(5000,i)}
save(out_5000_20, file="out_5000_20.rda")
```

Combine files

```{r}
temp <- c(out_500_1, out_500_2, out_500_3, out_500_4, out_500_5, out_500_6, out_500_7, out_500_8, out_500_9, out_500_10, out_500_11, out_500_12, out_500_13, out_500_14, out_500_15, out_500_16, out_500_17, out_500_18, out_500_19, out_500_20,
          out_1000_1, out_1000_2, out_1000_3, out_1000_4, out_1000_5, out_1000_6, out_1000_7, out_1000_8, out_1000_9, out_1000_10, out_1000_11, out_1000_12, out_1000_13, out_1000_14, out_1000_15, out_1000_16, out_1000_17, out_1000_18, out_1000_19, out_1000_20,
          out_5000_1, out_5000_2, out_5000_3, out_5000_4, out_5000_5, out_5000_6, out_5000_7, out_5000_8, out_5000_9, out_5000_10, out_5000_11, out_5000_12, out_5000_13, out_5000_14, out_5000_15, out_5000_16, out_5000_17, out_5000_18, out_5000_19, out_5000_20)
df_sim <- bind_rows(temp, .id = "column_label")
save(df_sim, file="df_sim.rda")

test_5000 <- filter(df_sim,N==5000)
test_1000 <- filter(df_sim,N==1000)
test_500 <- filter(df_sim,N==500)

```

function for calculating subgroup N
```{r}
sim_data_sub_N <- function(n,seed){
set.seed(seed)
    Sim<-data.frame(Race = sample(c(0,1,2,3, 4,5,6, 7,8, 9),n-40, replace = TRUE, prob=c(7380,22,156,320, 3100,224,138, 2048,3816, 28710)),
                      women = sample(c(0,1),n-40, replace = TRUE, prob=c(.64,.36)),
                      FG = sample(c(0,1),n-40, replace = TRUE, prob=c(.64,.36)))
minimums <- data.frame(Race = rep(0:9, 4),
                      women = rep(c(rep(0,10),rep(1,10)), 2),
                      FG = rep(c(rep(0,20), rep(1,20)),1))
    
    Sim <- rbind(Sim,minimums)
    
Sim <- Sim  %>%
  mutate(Asian = ifelse(Race==0 | Race ==1 | Race ==2| Race==3,1,0),
         Asian_Black = ifelse(Race==1,1,0),
         Asian_Hispanic = ifelse(Race==2,1,0),
         Asian_White = ifelse(Race==3,1,0),
         
         Black = ifelse(Race==4 | Race==5 |Race==6 |Race==1,1,0),
         Black_Hispanic = ifelse(Race==5,1,0),
         Black_White = ifelse(Race==6,1,0),
         
         Hispanic = ifelse(Race==7 | Race==8 | Race==2| Race==5,1,0),
         Hispanic_White = ifelse(Race==8,1,0),
         
         White = ifelse(Race==9 |Race ==3| Race==6| Race==8,1,0))
         
Sim <- Sim  %>%
  mutate(cluster = (1000000 + 100000*(Asian) +10000*(Black) +1000*(Hispanic) +100*(White) + 10*(women) + 1*(FG)))

N_sub <- Sim %>% group_by(cluster) %>%
  summarise(N_groups=n()) %>%
  mutate(group=c("CG White men","FG White men","CG White women","FG White women","CG Hispanic men","FG Hispanic men","CG Hispanic women","FG Hispanic women", "CG White Hispanic men","FG White Hispanic men","CG White Hispanic women", "FG White Hispanic women", "CG Black men","FG Black men","CG Black women","FG Black women","CG Black White men","FG Black White men","CG Black White women","FG Black White women", "CG Black Hispanic men","FG Black Hispanic men","CG Black Hispanic women","FG Black Hispanic women","CG Asian men","FG Asian men","CG Asian women","FG Asian women", "CG Asian White men","FG Asian White men","CG Asian White women", "FG Asian White women", "CG Asian Hispanic men","FG Asian Hispanic men","CG Asian Hispanic women","FG Asian Hispanic women","CG Asian Black men","FG Asian Black men","CG Asian Black women","FG Asian Black women"))  %>%
    arrange(match(group,c("CG Asian Black men", "CG Asian Black women", "CG Asian Hispanic men", "CG Asian Hispanic women", "CG Asian men", "CG Asian White men", "CG Asian White women", "CG Asian women",  
                         "CG Black Hispanic men", "CG Black Hispanic women", "CG Black men", "CG Black White men", "CG Black White women", "CG Black women",
                         "CG Hispanic men", "CG Hispanic women", "CG White Hispanic men", "CG White Hispanic women",
                         "CG White men", "CG White women",
                         "FG Asian Black men", "FG Asian Black women", "FG Asian Hispanic men", "FG Asian Hispanic women", "FG Asian men", "FG Asian White men", "FG Asian White women", "FG Asian women",
                         "FG Black Hispanic men", "FG Black Hispanic women", "FG Black men", "FG Black White men", "FG Black White women", "FG Black women",
                         "FG Hispanic men", "FG Hispanic women", "FG White Hispanic men", "FG White Hispanic women",
                         "FG White men", "FG White women")))

return(N_sub)}
```

Get N for subgroup
```{r}
N_500 <- foreach(i=1:1000) %dopar% {sim_data_sub_N(500,i)}
save(N_500, file="N_500.rda")

N_1000 <- foreach(i=1:1000) %dopar% {sim_data_sub_N(1000,i)}
save(N_1000, file="N_1000.rda")

N_5000 <- foreach(i=1:1000) %dopar% {sim_data_sub_N(5000,i)}
save(N_5000, file="N_5000.rda")

temp <- rep(c(N_500, N_1000, N_5000), each = 2)
temp_2 <- bind_rows(temp, .id = "column_label")
temp_2$group_sim <- temp_2$group
df <- cbind(df_sim,temp_2[,"N_groups"],temp_2[,"group_sim"])
save(df, file="df.rda")
```
