---
title: "CCMM sim"
output: html_document
date: '2022-07-03'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstan)
library(brms)
library(dplyr)
library(lme4)
library(tidyverse)
```

#For MLM models, follow parameters set by Evans & Erickson (SSM 2019)and Evans (SSM 2019)
#burn-in: 5000 iterations; total iterations:50,000 iterations; thinning: 50 iterations 
#sample size=100000

```{r}
n_big = 100000
n_realistic = 5000
seed=12345
core=4
course_enroll <- 50
```


This simulates data that is similar to our Physics data in the multidiscipline equity paper.
```{r}
set.seed (seed)
n <- n_big
    Sim<-data.frame(Race = sample(c(0,1,2,3,4),n, replace = TRUE, prob=c(.17,.07,.09,.77,.12)),
                      women = sample(c(0,1),n, replace = TRUE, prob=c(.64,.36)),
                      FG = sample(c(0,1),n, replace = TRUE, prob=c(.64,.36)))
Sim <- Sim  %>%
  mutate(Asian = ifelse(Race==0,1,0),
         Black = ifelse(Race==1,1,0),
         Hispanic = ifelse(Race==2,1,0),
         White = ifelse(Race==3,1,0),
         White_Hispanic = ifelse(Race==4,1,0),
         cluster = (10000000 + 1000000*(Asian) +100000*(Black) +10000*(Hispanic) +1000*(White) +100*(White_Hispanic) + 10*(women) + 1*(FG)),
         score = 47 - 3*FG -10*women -6*Black -10*Hispanic +2*White +3*FG*women +1*White_Hispanic -1*FG*Black +2*FG*Hispanic +2*FG*White -2*women*Black + 1*women*Hispanic -4*women*White - 1*FG*White_Hispanic + 5*women*White_Hispanic + 4*FG*women*Black + 1*FG*women*White - 1* FG*women*White_Hispanic + rnorm(n))
    Sim$course = rep(1:(n/course_enroll))
```

This simulates a set of majority White, even gender. Black = White (90%), women = men (50%)
```{r}
set.seed (seed)
    Sim_W<-data.frame(Black = sample(c(0,1),n, replace = TRUE, prob=c(0.9, 0.1)),
                      women = sample(c(0,1),n, replace = TRUE),
                      FG = sample(c(0,1),n, replace = TRUE))
    Sim_W$cluster <- (factor(100*(Sim_W$Black+1) + 10*(Sim_W$women+1) + 1*(Sim_W$FG+1)))

    Sim_W$int <- Sim_W$Black*Sim_even$women
    Sim_W$y = -Sim_W$Black + -Sim_W$women + -Sim_W$FG + -Sim_W$int + rnorm(n)
    Sim_W$course = (rep(1:(n/course_enroll))+n/course_enroll)
```

This simulates a set of majority Black, even gender. Black = White (10%), women = men (50%)
```{r}
set.seed (seed)
    Sim_B<-data.frame(  Black = sample(c(0,1),n, replace = TRUE, prob=c(0.9, 0.1)),
                      women = sample(c(0,1),n, replace = TRUE),
                      FG = sample(c(0,1),n, replace = TRUE))
    Sim_B$cluster <- (factor(100*(Sim_B$Black+1) + 10*(Sim_B$women+1) + 1*(Sim_B$FG+1)))

    Sim_B$int <- Sim_B$Black*Sim_even$women
    Sim_B$y = -Sim_B$Black + -Sim_B$women + -Sim_B$FG + -Sim_B$int + rnorm(n)
    Sim_B$course = (rep(1:(n/course_enroll))+2*n/course_enroll)
```

Create schools samples (10,000 students, 50/course)
```{r}
Students <- 10000
Data_even <- filter(Sim_even, course<=(Students/course_enroll))
Data_W <- filter(Sim_W, course<=(Students/course_enroll + n/course_enroll))
temp <- rbind(Sim_W, Sim_B)
Data_mix <- filter(temp, course<=(0.9*Students/course_enroll + n/course_enroll) 
                   | course>(3*n/course_enroll-0.1*Students/course_enroll))

```

############################## Scenario 1 ###################################
All even courses (no course nesting)
```{r}
    ###############OLS REGRESSION without interaction term
OLS_even <- lm(y ~ Black + women + FG, data = Data_even)
    OLScoeff_even <- summary(OLS_even)$coefficients[,1]
    OLScoeffSE_even <- summary(OLS_even)$coefficients[,2]
    OLScoeff_even <- cbind(OLScoeff_even, OLScoeffSE_even)
save(OLS_even, file="~/MAIHDA/Model_output/OLS_even.rda")
save(OLScoeff_even, file="~/MAIHDA/Coefficients/OLScoeff_even.rda")
    
    ###############OLS REGRESSION with interaction term
OLS_int_even <- lm(y ~ Black + women + FG + Black*women, data = Data_even)
    OLS_intcoeff_even <- summary(OLS_int_even)$coefficients[,1]
    OLS_intcoeffSE_even <- summary(OLS_int_even)$coefficients[,2]
    OLS_intcoeff_even <- cbind(OLS_intcoeff_even, OLS_intcoeffSE_even)
    save(OLS_int_even, file="~/MAIHDA/Model_output/OLS_int_even.rda")
        save(OLS_intcoeff_even, file="~/MAIHDA/Coefficients/OLSintcoeff_even.rda")
    
    ###############MAIHDA, without interaction term
    MLM_even<- brm(formula= y ~ Black + women +FG + (1|cluster), data=Data_even, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main and randoms effects coefficients
fix_MLM_even<-    fixef(MLM2_even)
ran_MLM_even<-    ranef(MLM2_even)$cluster
save(fix_MLM_even, file="~/MAIHDA/Coefficients/fix_MLM_even.rda")
save(ran_MLM_even, file="~/MAIHDA/Coefficients/ran_MLM_even.rda")
save(MLM_even, file="~/MAIHDA/Model_output/MLM_even.rda")
    
    ###############MAIHDA, with interaction term
    MLM_int_even<- brm(formula= y ~ Black + women +FG + Black:women + (1|cluster), data=Data_even, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main effects coefficients
    fix_MLM_int_even<-    fixef(MLMint2_even)
ran_MLMint_even<-    ranef(MLMint2_even)$cluster
save(fix_MLM_int_even, file="~/MAIHDA/Coefficients/fix_MLM_int_even.rda")
save(ran_MLM_int_even, file="~/MAIHDA/Coefficients/ran_MLM_int_even.rda")
save(MLM_int_even, file="~/MAIHDA/Model_output/MLMint_even.rda")
    
```

############################## Scenario 2 ###################################
All even courses - CCMM
```{r}
    ###############OLS REGRESSION without interaction term
OLS_even_ccmm <- lmer(y ~ Black + women + FG + (1|course), data = Data_even)
    OLScoeff_even_ccmm <- summary(OLS_even_ccmm)$coefficients[,1]
    OLScoeffSE_even_ccmm <- summary(OLS_even_ccmm)$coefficients[,2]
    OLScoeff_even_ccmm_ccmm <- cbind(OLScoeff_even_ccmm, OLScoeffSE_even_ccmm)
save(OLS_even_ccmm, file="~/MAIHDA/Model_output/OLS_even_ccmm.rda")
save(OLScoeff_even_ccmm, file="~/MAIHDA/Coefficients/OLScoeff_even_ccmm.rda")
    
    ###############OLS REGRESSION with interaction term
OLS_int_even_ccmm <- lmer(y ~ Black + women + FG + Black*women + (1|course), data = Data_even)
    OLS_intcoeff_even_ccmm <- summary(OLS_int_even_ccmm)$coefficients[,1]
    OLS_intcoeffSE_even_ccmm <- summary(OLS_int_even_ccmm)$coefficients[,2]
    OLS_intcoeff_even_ccmm <- cbind(OLS_intcoeff_even_ccmm, OLS_intcoeffSE_even_ccmm)
    save(OLS_int_even_ccmm, file="~/MAIHDA/Model_output/OLS_int_even_ccmm.rda")
        save(OLS_intcoeff_even_ccmm, file="~/MAIHDA/Coefficients/OLSintcoeff_even_ccmm.rda")
    
    ###############MAIHDA, without interaction term
    MLM_even_ccmm<- brm(formula= y ~ Black + women +FG + (1|cluster) + (1|course), data=Data_even_ccmm, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main and randoms effects coefficients
fix_MLM_even_ccmm<-    fixef(MLM2_even_ccmm)
ran_MLM_even_ccmm<-    ranef(MLM2_even_ccmm)$cluster
save(fix_MLM_even_ccmm, file="~/MAIHDA/Coefficients/fix_MLM_even_ccmm.rda")
save(ran_MLM_even_ccmm, file="~/MAIHDA/Coefficients/ran_MLM_even_ccmm.rda")
save(MLM_even_ccmm, file="~/MAIHDA/Model_output/MLM_even_ccmm.rda")
    
    ###############MAIHDA, with interaction term
    MLM_int_even_ccmm<- brm(formula= y ~ Black + women +FG + Black:women + (1|cluster) + (1|course), data=Data_even_ccmm, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main effects coefficients
    fix_MLM_int_even_ccmm<-    fixef(MLMint2_even_ccmm)
ran_MLMint_even_ccmm<-    ranef(MLMint2_even_ccmm)$cluster
save(fix_MLM_int_even_ccmm, file="~/MAIHDA/Coefficients/fix_MLM_int_even_ccmm.rda")
save(ran_MLM_int_even_ccmm, file="~/MAIHDA/Coefficients/ran_MLM_int_even_ccmm.rda")
save(MLM_int_even_ccmm, file="~/MAIHDA/Model_output/MLMint_even_ccmm.rda")
```


############################## Scenario 3 ###################################
White courses (no course nesting)
```{r}
    ###############OLS REGRESSION without interaction term
OLS_W <- lm(y ~ Black + women + FG, data = Data_W)
    OLScoeff_W <- summary(OLS_W)$coefficients[,1]
    OLScoeffSE_W <- summary(OLS_W)$coefficients[,2]
    OLScoeff_W <- cbind(OLScoeff_W, OLScoeffSE_W)
save(OLS_W, file="~/MAIHDA/Model_output/OLS_W.rda")
save(OLScoeff_W, file="~/MAIHDA/Coefficients/OLScoeff_W.rda")
    
    ###############OLS REGRESSION with interaction term
OLS_int_W <- lm(y ~ Black + women + FG + Black*women, data = Data_W)
    OLS_intcoeff_W <- summary(OLS_int_W)$coefficients[,1]
    OLS_intcoeffSE_W <- summary(OLS_int_W)$coefficients[,2]
    OLS_intcoeff_W <- cbind(OLS_intcoeff_W, OLS_intcoeffSE_W)
    save(OLS_int_W, file="~/MAIHDA/Model_output/OLS_int_W.rda")
        save(OLS_intcoeff_W, file="~/MAIHDA/Coefficients/OLSintcoeff_W.rda")
    
    ###############MAIHDA, without interaction term
    MLM_W<- brm(formula= y ~ Black + women +FG + (1|cluster), data=Data_W, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main and randoms effects coefficients
fix_MLM_W<-    fixef(MLM2_W)
ran_MLM_W<-    ranef(MLM2_W)$cluster
save(fix_MLM_W, file="~/MAIHDA/Coefficients/fix_MLM_W.rda")
save(ran_MLM_W, file="~/MAIHDA/Coefficients/ran_MLM_W.rda")
save(MLM_W, file="~/MAIHDA/Model_output/MLM_W.rda")
    
    ###############MAIHDA, with interaction term
    MLM_int_W<- brm(formula= y ~ Black + women +FG + Black:women + (1|cluster), data=Data_W, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main effects coefficients
    fix_MLM_int_W<-    fixef(MLMint2_W)
ran_MLMint_W<-    ranef(MLMint2_W)$cluster
save(fix_MLM_int_W, file="~/MAIHDA/Coefficients/fix_MLM_int_W.rda")
save(ran_MLM_int_W, file="~/MAIHDA/Coefficients/ran_MLM_int_W.rda")
save(MLM_int_W, file="~/MAIHDA/Model_output/MLMint_W.rda")
  
```

############################## Scenario 4 ###################################
White courses - CCMM
```{r}
    ###############OLS REGRESSION without interaction term
OLS_W_ccmm <- lmer(y ~ Black + women + FG + (1|course), data = Data_W)
    OLScoeff_W_ccmm <- summary(OLS_W_ccmm)$coefficients[,1]
    OLScoeffSE_W_ccmm <- summary(OLS_W_ccmm)$coefficients[,2]
    OLScoeff_W_ccmm_ccmm <- cbind(OLScoeff_W_ccmm, OLScoeffSE_W_ccmm)
save(OLS_W_ccmm, file="~/MAIHDA/Model_output/OLS_W_ccmm.rda")
save(OLScoeff_W_ccmm, file="~/MAIHDA/Coefficients/OLScoeff_W_ccmm.rda")
    
    ###############OLS REGRESSION with interaction term
OLS_int_W_ccmm <- lmer(y ~ Black + women + FG + Black*women + (1|course), data = Data_W)
    OLS_intcoeff_W_ccmm <- summary(OLS_int_W_ccmm)$coefficients[,1]
    OLS_intcoeffSE_W_ccmm <- summary(OLS_int_W_ccmm)$coefficients[,2]
    OLS_intcoeff_W_ccmm <- cbind(OLS_intcoeff_W_ccmm, OLS_intcoeffSE_W_ccmm)
    save(OLS_int_W_ccmm, file="~/MAIHDA/Model_output/OLS_int_W_ccmm.rda")
        save(OLS_intcoeff_W_ccmm, file="~/MAIHDA/Coefficients/OLSintcoeff_W_ccmm.rda")
    
    ###############MAIHDA, without interaction term
    MLM_W_ccmm<- brm(formula= y ~ Black + women +FG + (1|cluster) + (1|course), data=Data_W_ccmm, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main and randoms effects coefficients
fix_MLM_W_ccmm<-    fixef(MLM2_W_ccmm)
ran_MLM_W_ccmm<-    ranef(MLM2_W_ccmm)$cluster
save(fix_MLM_W_ccmm, file="~/MAIHDA/Coefficients/fix_MLM_W_ccmm.rda")
save(ran_MLM_W_ccmm, file="~/MAIHDA/Coefficients/ran_MLM_W_ccmm.rda")
save(MLM_W_ccmm, file="~/MAIHDA/Model_output/MLM_W_ccmm.rda")
    
    ###############MAIHDA, with interaction term
    MLM_int_W_ccmm<- brm(formula= y ~ Black + women +FG + Black:women + (1|cluster) + (1|course), data=Data_W_ccmm, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main effects coefficients
    fix_MLM_int_W_ccmm<-    fixef(MLMint2_W_ccmm)
ran_MLMint_W_ccmm<-    ranef(MLMint2_W_ccmm)$cluster
save(fix_MLM_int_W_ccmm, file="~/MAIHDA/Coefficients/fix_MLM_int_W_ccmm.rda")
save(ran_MLM_int_W_ccmm, file="~/MAIHDA/Coefficients/ran_MLM_int_W_ccmm.rda")
save(MLM_int_W_ccmm, file="~/MAIHDA/Model_output/MLMint_W_ccmm.rda")
```

############################## Scenario 5 ###################################
Mix courses (no course nesting)
```{r}
    ###############OLS REGRESSION without interaction term
OLS_mix <- lm(y ~ Black + women + FG, data = Data_mix)
    OLScoeff_mix <- summary(OLS_mix)$coefficients[,1]
    OLScoeffSE_mix <- summary(OLS_mix)$coefficients[,2]
    OLScoeff_mix <- cbind(OLScoeff_mix, OLScoeffSE_mix)
save(OLS_mix, file="~/MAIHDA/Model_output/OLS_mix.rda")
save(OLScoeff_mix, file="~/MAIHDA/Coefficients/OLScoeff_mix.rda")
    
    ###############OLS REGRESSION with interaction term
OLS_int_mix <- lm(y ~ Black + women + FG + Black*women, data = Data_mix)
    OLS_intcoeff_mix <- summary(OLS_int_mix)$coefficients[,1]
    OLS_intcoeffSE_mix <- summary(OLS_int_mix)$coefficients[,2]
    OLS_intcoeff_mix <- cbind(OLS_intcoeff_mix, OLS_intcoeffSE_mix)
    save(OLS_int_mix, file="~/MAIHDA/Model_output/OLS_int_mix.rda")
        save(OLS_intcoeff_mix, file="~/MAIHDA/Coefficients/OLSintcoeff_mix.rda")
    
    ###############MAIHDA, without interaction term
    MLM_mix<- brm(formula= y ~ Black + women +FG + (1|cluster), data=Data_mix, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main and randoms effects coefficients
fix_MLM_mix<-    fixef(MLM2_mix)
ran_MLM_mix<-    ranef(MLM2_mix)$cluster
save(fix_MLM_mix, file="~/MAIHDA/Coefficients/fix_MLM_mix.rda")
save(ran_MLM_mix, file="~/MAIHDA/Coefficients/ran_MLM_mix.rda")
save(MLM_mix, file="~/MAIHDA/Model_output/MLM_mix.rda")
    
    ###############MAIHDA, with interaction term
    MLM_int_mix<- brm(formula= y ~ Black + women +FG + Black:women + (1|cluster), data=Data_mix, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main effects coefficients
    fix_MLM_int_mix<-    fixef(MLMint2_mix)
ran_MLMint_mix<-    ranef(MLMint2_mix)$cluster
save(fix_MLM_int_mix, file="~/MAIHDA/Coefficients/fix_MLM_int_mix.rda")
save(ran_MLM_int_mix, file="~/MAIHDA/Coefficients/ran_MLM_int_mix.rda")
save(MLM_int_mix, file="~/MAIHDA/Model_output/MLMint_mix.rda")
  
```

############################## Scenario 6 ###################################
Mix courses - CCMM
```{r}
    ###############OLS REGRESSION without interaction term
OLS_mix_ccmm <- lmer(y ~ Black + women + FG + (1|course), data = Data_mix)
    OLScoeff_mix_ccmm <- summary(OLS_mix_ccmm)$coefficients[,1]
    OLScoeffSE_mix_ccmm <- summary(OLS_mix_ccmm)$coefficients[,2]
    OLScoeff_mix_ccmm_ccmm <- cbind(OLScoeff_mix_ccmm, OLScoeffSE_mix_ccmm)
save(OLS_mix_ccmm, file="~/MAIHDA/Model_output/OLS_mix_ccmm.rda")
save(OLScoeff_mix_ccmm, file="~/MAIHDA/Coefficients/OLScoeff_mix_ccmm.rda")
    
    ###############OLS REGRESSION with interaction term
OLS_int_mix_ccmm <- lmer(y ~ Black + women + FG + Black*women + (1|course), data = Data_mix)
    OLS_intcoeff_mix_ccmm <- summary(OLS_int_mix_ccmm)$coefficients[,1]
    OLS_intcoeffSE_mix_ccmm <- summary(OLS_int_mix_ccmm)$coefficients[,2]
    OLS_intcoeff_mix_ccmm <- cbind(OLS_intcoeff_mix_ccmm, OLS_intcoeffSE_mix_ccmm)
    save(OLS_int_mix_ccmm, file="~/MAIHDA/Model_output/OLS_int_mix_ccmm.rda")
        save(OLS_intcoeff_mix_ccmm, file="~/MAIHDA/Coefficients/OLSintcoeff_mix_ccmm.rda")
    
    ###############MAIHDA, without interaction term
    MLM_mix_ccmm<- brm(formula= y ~ Black + women +FG + (1|cluster) + (1|course), data=Data_mix_ccmm, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main and randoms effects coefficients
fix_MLM_mix_ccmm<-    fixef(MLM2_mix_ccmm)
ran_MLM_mix_ccmm<-    ranef(MLM2_mix_ccmm)$cluster
save(fix_MLM_mix_ccmm, file="~/MAIHDA/Coefficients/fix_MLM_mix_ccmm.rda")
save(ran_MLM_mix_ccmm, file="~/MAIHDA/Coefficients/ran_MLM_mix_ccmm.rda")
save(MLM_mix_ccmm, file="~/MAIHDA/Model_output/MLM_mix_ccmm.rda")
    
    ###############MAIHDA, with interaction term
    MLM_int_mix_ccmm<- brm(formula= y ~ Black + women +FG + Black:women + (1|cluster) + (1|course), data=Data_mix_ccmm, seed=seed, cores=core, iter=50000, warmup = 5000, thin = 50)
    #extract main effects coefficients
    fix_MLM_int_mix_ccmm<-    fixef(MLMint2_mix_ccmm)
ran_MLMint_mix_ccmm<-    ranef(MLMint2_mix_ccmm)$cluster
save(fix_MLM_int_mix_ccmm, file="~/MAIHDA/Coefficients/fix_MLM_int_mix_ccmm.rda")
save(ran_MLM_int_mix_ccmm, file="~/MAIHDA/Coefficients/ran_MLM_int_mix_ccmm.rda")
save(MLM_int_mix_ccmm, file="~/MAIHDA/Model_output/MLMint_mix_ccmm.rda")
```


